\documentclass{article}
\title{Demo}
\author{cyprien taib}
\date{February 2021}

\begin{document}

    \maketitle
    \section{introduction}
        
    In this document we will see how we proced the task and why we make the golang chose for programming, after that we will speak about the tools we use.


    The projet is on our github in two part, first part is purlly the backend and maybe in the future the front end in two separates files. \newline\newline

    The seconde part is functionnal, it permit to create table, fill it and run it. We have also put a docker file to create the mysql server and PhpMyAdmin.
   
    
    \section{Backend Part}

    We choose golang for the backend because is more efficency and fastest than python. 

    We enter in the Backend file witch contains files and folders.

    The .air.toml we see is a config file for auto reload the API.

    The config.yaml is the config file for the API.

    The file go.mod and go.sum is for the golang modules.

    We see a directory named internal.

        In internal

    we see three directories
        \begin{enumerate}
            \item http
            \item sql request
            \item utils
        \end{enumerate}

    the utils is for loadding configuration into the server \newline\newline

    the folder http contains two directories and one file " http.go ". The file is like the main file for running the API.  

    The folder middlewares contain securty constrain and controllers all the handler for the API. \newline\newline

    Back to the sql request folder, it contains just all the code for making request to the data base. \newline\newline

    Each tables have it handler and it sql request file. \newline
    
    \section{Request Possibillity}

    \begin{itemize}
        \item List of company aircraft
        \item List of Sup Air Line pilots
        \item List of personnel by category
        \item List of passengers per flight
        \item List of flights to a given city
        \item List of departures for the day
        \item List of cities served by Sup Air Line
        \item List of destinations served by a captain
        \item List of pilots whose license must be renewed
        \item Lists of regular passengers who fly more than 2 flights / month
        \item Professions with the most regular passengers
        \item Number of hours worked by a captain
        \item Number of flight hours of each aircraft
        \item Number of passengers transported by plane over a given period
        \item Number of passengers carried over a given period
        \item Number of tickets sold per day / week / month
        \item Total sales
        \item Average flights per pilot
        \item Most profitable destinations (high occupancy rate)
        \item Average occupancy rate by plane / flight / destination
        \item Which pilots fly to their city
        \item Create Data for all tables
        \item Update Data for all tables
        \item Delete Data for all tables 
    \end{itemize}

\end{document}